Quantitative, Multispecies Monitoring at a Continental Scale

### 2025-02-25 Priors table.tex

&Parameters&\\
\hline
$\psi$& overall mean hake eDNA concentration (copies/$\mu$L) & $\mathcal{N}(2,2)$\\
$\epsilon_{(x,y,d)}$& spatial and depth specific random effect & $\mathcal{N}(0,\sigma_D)$\\
$\sigma_D= (0, +\infty)$& standard deviation of spatial and depth specific random effect & $\mathcal{N}(0,3)$\\

>>>>

&Parameters&\\
\hline
$\psi$& overall mean hake eDNA concentration (copies/L) & $\mathcal{N}(2,2)$\\
$\epsilon_{(x,y,d)}$& spatial and depth specific random effect & $\mathcal{N}(0,\sigma_D)$\\
$\sigma_D= (0, +\infty)$& standard deviation of spatial and depth specific random effect & $\mathcal{N}(0,3)$\\
